Improving Cell Segmentation and Tracking via Mechanistic Models of Rod-Shaped Bacteria

### 2025-09-15 paper_segmentation_tracking/main.tex
formatting
move tabular further up; add smudges

\pagebreak
\renewcommand{\contentsname}{Table of Contents (remove before submission)}
\tableofcontents
\vfill
\pagebreak

@@

@@

\begin{table}[H]
    \begin{tabularx}{\columnwidth}{l l}
        \toprule
        Microscopic effect & Image Transformation\\
        \midrule
        Sensor Noise & White noise on pixel level\\
        Shaking Apparatus & Random spatial translations between time-steps\\
        Lighting & 3D Rendering: Introcue light sources; modify surface of cells; use \ac{pbr}\\
        Cellular Translucency & Make cells partially transparent\\
        Depth of Field & Included in \ac{pbr}\\
        \bottomrule
    \end{tabularx}
    \label{tabular:microscopic-image-defects}
\end{table}

>>>>

% TODO comment this before submission
\vfill
\pagebreak
\renewcommand{\contentsname}{Table of Contents (remove before submission)}
\tableofcontents
\vfill
\pagebreak

@@

\begin{table}[H]
    \begin{tabularx}{\textwidth}{l l}
        \toprule
        Microscopic effect & Image Transformation\\
        \midrule
        Sensor Noise & White noise on pixel level\\
        Shaking Apparatus & Random spatial translations between time-steps\\
        Smudges & Custom overlays (Rotations, Mirrors, Combinations, etc.)\\
        Lighting & 3D Rendering: Introcue light sources; modify surface of cells; use \ac{pbr}\\
        Cellular Translucency & Make cells partially transparent\\
        Depth of Field & Included in \ac{pbr}\\
        \bottomrule
    \end{tabularx}
    \label{tabular:microscopic-image-defects}
\end{table}

@@
